Sequential rank agreement methods for comparison of ranked lists

### 2015-04-10 latex/paper.Rnw
Text

We cannot directly compute $A(p)$ for all predictors because we only observe a censored version of $\tilde R$ for some of the lists. Instead we assume that the rank assigned to predictor $p$ in list $l$ is uniformly distributed among the ranks that have been unassigned for list $l$. The ranks are clearly not independent since each of the lists essentially contains full set of ranks

@@

@@

>>>>

We cannot directly compute $A(p)$ for all predictors because we only
observe a censored version of $\tilde R$ for some of the
lists. Instead we assume that the rank assigned to predictor $p$ in
list $l$ is uniformly distributed among the ranks that have \emph{not}
been assigned for list $l$.

The rankings within a single list are clearly not independent since each of the lists
essentially contains full set of ranks

@@

<<>>=
library(SuperRanker)
@

@@

\section{Alternatives}
